MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-08-22 chapters/MetaTracts.tex
updated images

\section {Voxelization and surface extraction}
\label{sec:vis}
Apart from direct visualization of the MetaTracts, we show two simple extensions of MetaTracts. The first way is to voxelize the original volume according to the clusters each voxel is associated with.
The second is to extract the corresponding surfaces from the voxel data by binarizing the volume per cluster and extracting the isosurface from the binary volume by marching cubes algorithm. To voxelize the space,  we compute a neighborhood around each voxel. We then enumerate the number of voxels of each class (cluster) in this neighborhood. The voxel is then assigned to the class with the maximum number of elements in the neighborhood.  Intuitively this is a modification of the flood-fill algorithm. Figure~\ref{fig:mesh} and ~\ref{fig:prepreg}D shows examples od extracted meshes.

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/all_clusters.PNG}
	\caption{(A) Orientation wise decomposition of data set Figure~\ref{fig:data-char}A into the extracted bundles and (B) all of them combined.}
	\label{fig:crop-16-decomp}
\end{figure}
\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/crop-6-J.PNG}
	\caption{Data set with flat thin and compact bundles. A shows the volume rendering and a 2D slice, B shows the clusters according to individual orientation.C shows the complete result. D shows the cropped part of the mesh generated from the marked bundle.}
	\label{fig:prepreg}
\end{figure}
\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/Graph_crop16_2.PNG}
	\caption{Number of tracts and median, minimum and maximum length of individual MetaTracts in the orientation cluster Figure~\ref{fig:orientation_clustering}C clustered into 10 clusters. The unit for length is the grid cube length. Figure~\ref{fig:length_distribution}(b) shows the length of individual MetaTracts in cluster 6.}
	\label{fig:len_dist_crop16}
\end{figure}

>>>>

\section {Voxelization and surface extraction}
\label{sec:vis}
Apart from direct visualization of the MetaTracts, we show two simple extensions of MetaTracts. The first way is to voxelize the original volume according to the clusters each voxel is associated with.
The second is to extract the corresponding surfaces from the voxel data by binarizing the volume per cluster and extracting the isosurface from the binary volume by marching cubes algorithm. To voxelize the space,  we compute a neighborhood around each voxel. We then enumerate the number of voxels of each class (cluster) in this neighborhood. The voxel is then assigned to the class with the maximum number of elements in the neighborhood.  Intuitively this is a modification of the flood-fill algorithm. Figure~\ref{fig:mesh} and Fig.~\ref{fig:prepreg}D shows examples od extracted meshes.

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/all_clusters.PNG}
	\caption{(A) Orientation wise decomposition of data set Figure~\ref{fig:data-char}A into the extracted bundles and (B) all of them combined.}
	\label{fig:crop-16-decomp}
\end{figure}
\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/crop-6-J.PNG}
	\caption{Data set with flat thin and compact bundles. A shows the volume rendering and a 2D slice, B shows the clusters according to individual orientation.C shows the complete result. D shows the cropped part of the mesh generated from the marked bundle.}
	\label{fig:prepreg}
\end{figure}
\begin{figure}
\centering
	\includegraphics[width=0.5\textwidth]{imagesMT2014/Graph_crop16.PNG}
	\caption{Number of tracts and median, minimum and maximum length of individual MetaTracts in the orientation cluster Fig.~\ref{fig:orientation_clustering}C, clustered into 10 clusters (Fig.~\ref{fig:crop-16-decomp}A top). The unit for length is the grid cube length. Figure~\ref{fig:length_distribution}(b) shows the length of individual MetaTracts in cluster 6.}
	\label{fig:len_dist_crop16}
\end{figure}
